The \dealii Library, Version 9.5

### 2023-05-27 9.5/paper.tex
More minor changes.

In the current release, LinearAlgebra::distributed::Vector and the
CUDAWrappers::MatrixFree framework are using Kokkos. This allows them to work on
all the architectures supported by Kokkos. The Kokkos backend used \dealii is
`Kokkos::DefaultExecutionSpace` which is the highest available in the hierarchy
device, host-parallel, and host-serial.

@@

There are also two new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item The program \textit{``A posteriori error estimator for first order hyperbolic problems''}
  was contributed by Marco Feder.
  \item The program \textit{``Distributed moving laser heating''} was contributed by
  Hongfeng Ma and Tatiana E.~Itina.
\end{itemize}

\todo[inline]{There may be another one by Sam Scheuerman. Let's see
  whether it still arrives in time.}

>>>>

In the current release, LinearAlgebra::distributed::Vector and the
CUDAWrappers::MatrixFree framework are using Kokkos. This allows them to work on
all the architectures supported by Kokkos. The Kokkos backend used by \dealii is
\texttt{Kokkos::DefaultExecutionSpace} which is the highest available in the hierarchy
device, host-parallel, and host-serial.

\todo[inline]{Are you saying that all three of these are used? If so,
  maybe replace ``backend'' by ``backends''?}

\todo[inline]{Would it be useful to add a paragraph about future plans?}

@@

There are also three new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item \textit{``A posteriori error estimator for first order hyperbolic problems''},
  contributed by Marco Feder;
  \item \textit{``Distributed moving laser heating''}, contributed by
  Hongfeng Ma and Tatiana E.~Itina;
  \item \textit{``Generalized Swift-Hohenberg Equation Solver''}, contributed by
  Sam Scheuerman.
\end{itemize}
